---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# BrAPI R package 
<!--
[![Build status](https://ci.appveyor.com/api/projects/status/7qsrpldj8g3m3lu3?svg=true)](https://ci.appveyor.com/project/cipriuhq/brapi)
[![Build Status](https://travis-ci.org/CIP-RIU/brapi.svg?branch=master)](https://travis-ci.org/CIP-RIU/brapi)
[![Coverage Status](https://img.shields.io/codecov/c/github/CIP-RIU/brapi/master.svg)](https://codecov.io/github/CIP-RIU/brapi?branch=master)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/brapi)](https://cran.r-project.org/package=brapi)
[![lifecycle](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
-->

This version is still under development. The implementation sometimes changes minor details with respect to the GET calls. The POST and PUT calls are under construction!

Current support is mainly for BrAPI version 1.3

Development of version 2.0 will start shortly after the Production release.

<!--A 176 tests have been implemented to check on compliance.-->

For independent checks against a database you may use http://webapps.ipk-gatersleben.de/brapivalidator.

It seems several databases may not currently be fully accessible due to protocol changes. 

```{r label="read-me-setup", echo=FALSE, eval=TRUE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-")
```

# README
An R package to use the [Breeding API (BrAPI)](https://brapi.org/documentation) for accessing BrAPI compliant plant breeding data.
<!--See the [documentation](https://cip-riu.github.io/brapi/) for details.-->

It can be installed using:

```{r, eval=FALSE}
install.packages("remotes")
remotes::install_github("mverouden/brapir")
```

<!--## How to use the package
See [tutorial](https://cip-riu.github.io/brapi/articles/tutorial.html).-->
